
\documentclass[10pt,a4paper,ragged2e,withhyper]{altacv}

%% AltaCV uses the fontawesome5 package.

\geometry{left=1.25cm,right=1.25cm,top=1.5cm,bottom=1.5cm,columnsep=1.2cm}

\usepackage{paracol}
\usepackage{array}
\usepackage{tabularx}

\ifxetexorluatex
  \setmainfont{Lato}
\else
  \usepackage[default]{lato}
\fi

\definecolor{VividPurple}{HTML}{6A0F8E}
\definecolor{SlateGrey}{HTML}{6A0F8E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{VividPurple}
\colorlet{headingrule}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\input{pubs-num}

%% sample.bib contains your publications
\addbibresource{sample.bib}

\begin{document}
\name{Muhammad Affan Wahid}

\personalinfo{%
  \begin{tabular}{@{}p{7.4cm} p{7.4cm} p{7.4cm}@{}}
    \vspace*{-3mm}\email{mohammadaffanwahid@gmail.com} & \faPhone\ {+92 3024755039} & \faGlobe\ \href{https://affanwahid.com}{\texttt{affanwahid.com}} \\
    \github{mohammadaffanwahid} & \linkedin{muhammad-affan-wahid} & \location{Lahore, Pakistan} \\
  \end{tabular}


}

\makecvheader

\AtBeginEnvironment{itemize}{\small}

\columnratio{0.6}

\begin{paracol}{2}

\cvsection{Work Experience}

\cvevent{\textbf{Agentic AI Team Lead}}{Hire a Bot}{Jan 2026 -- Current}{Lahore}
\begin{itemize}
    \item Managing a team of 4 engineers to develop an Agentic AI chat and voice bot SaaS platform from scratch.
    \item Architecting and launching a fully autonomous voice and chat agent platform with seamless third-party service integration to manage end-to-end customer workflows.
\end{itemize}

\divider

\cvevent{\textbf{Senior Python Developer}}{Turing}{Oct 2024 -- Jan 2026}{Remote}
\begin{itemize}
    \item Enhanced Meta's Llama 4 with RLHF (Reinforcement Learning Through Human Feedback) for single and multi-turn conversations.
    \item Stayed Top Performer in a team of 98 people for five consecutive weeks through impactful contributions to project milestones and outcomes. Gained special permission to work on the weekends as a bonus.
    \item Created high quality and detailed dataset for training Google's Gemini 2.5 Flash.
    \item Developed training data for agentic AI models across PayPal, Slack, Google Drive, Calendar, Microsoft Teams, and Gmail; received bonus hours for consistently maintaining high-quality work.
\end{itemize}

\divider

\cvevent{\textbf{Software Engineer}}{Educative, Inc.}{June 2023 -- May 2024}{Lahore, Pakistan}
\begin{itemize}
    \item Created the interview vertical front and back end, opening a robust new funnel and stable revenue avenues.
    \item Integrated Hubspot to streamline Userback and support top-notch user feedback functionality.
    \item Created a pipeline to collect custom metric data using OTEL and integrated it with Google Dashboards for visualization.
    \item Translated Figma blueprints into a seamless, production-ready Next.js experience and led code reviews to maintain quality.
\end{itemize}

\divider

\cvevent{\textbf{Computer Vision Intern}}{Hazen.ai}{Nov 2022 -- Jan 2023}{Lahore, Pakistan}
\begin{itemize}
\item Created an automatic framework for synthetic license plate datasets across multiple countries to minimize human effort and maximize productivity.
\end{itemize}

\divider

\cvevent{\textbf{Research Intern}}{Intelligent Machines Lab ITU}{Jul 2021 -- Oct 2021}{Lahore, Pakistan}
\begin{itemize}
\item Engaged in intricate labeling of malaria cell data used in a CVPR-published research paper titled \textbf{"Towards Low-Cost and Efficient Malaria Detection,"} earning acknowledgment.
\end{itemize}

\switchcolumn
\cvsection{Education}
\cvevent{BS in Computer Science}{Information Technology University}{2019-2023}{Lahore, Pakistan}
\divider
\cvevent{FSc Pre-Engineering}{Fazaia Intermediate College}{Aug 2017-Nov 2019}{Lahore, Pakistan}
\divider
\cvevent{Matriculation}{Fazaia Intermediate College}{Jun 2015-Aug 2017}{Lahore, Pakistan}

\cvsection{Technical Skills}
        \cvtag{Python}\cvtag{Django}\cvtag{LangChain}\cvtag{LangGraph}\cvtag{Agentic AI}\cvtag{Vector Databases}\cvtag{Voice Bots}\cvtag{Chatbots}\cvtag{ReactJS}\cvtag{NextJS}\cvtag{JavaScript}

\cvsection{Extracurricular}
    \textbf{Co-Founder Kaar-e-kamal ITU (2022-current)}
        \begin{itemize}
            \item Created this chapter from scratch providing free education, food, and medicine to the needy ones.
        \end{itemize}
    \textbf{Treasurer GDSC-ITU (2022-2023)}
        \begin{itemize}
            \item Organized the funds of many events for the developers including CodeRush coding competition.
        \end{itemize}
    \textbf{Treasurer IEEE-ITU (2022-2023)}
        \begin{itemize}
            \item Organized the funds of many events for the engineers including IEEEXtreme coding competition.
        \end{itemize}
\cvsection{Achievements}
    \textbf{1st position}
        \begin{itemize}
            \item  Programming Competition at Superior Technical
Symposium 2021.
        \end{itemize}

    \textbf{1st position}
        \begin{itemize}
            \item Atchison College AI Competition.
        \end{itemize}
        
    \textbf{2nd position}
        \begin{itemize}
            \item All over Pakistan in IEEE Extreme Programming Competition
2021.
        \end{itemize}

    \textbf{2nd position}
        \begin{itemize}
            \item position at GDSC Code Rush programming competition held at
ITU.
        \end{itemize}
    \textbf{3rd position}
        \begin{itemize}
            \item at the IEEE Code Camp held at UET.
        \end{itemize}
\end{paracol}

\end{document}
